\tool: Revisiting BadUSB with Type-C

### 2021-01-30 WOOT/Files/experiment.tex
Done with Experiments Section

In the manual analysis, we replayed the videos and extracted sensitive information.
The data we collected are listed in Table~\ref{table:information_extracted}.
Accounts of internet applications such as Apple, iCloud, Facebook, Twitter, etc. can be obtained.
Moreover, all of the typing inputs on the virtual keyboard, including the system keyboard and the built-in security keyboard of the financial applications, can be clearly recorded.
We can obtain the plain text of passwords such as WiFi passwords.
Furthermore, the received SMS verification code (usually used to confirm real-name authentication) can be obtained when it appears in the top notification bar.

In summary, though we can't directly obtain the user's password on the lock screen, we can still check all of the information presented on the screen, extract private information including but not limited to social accounts, bank accounts, personal financial situation, etc., if the user unconsciously unlocks the screen.
It is worth mentioning that, those \textit{secure keyboards} built in some financial apps just disrupt keyboard sequences, they can't prevent attacks similar as \tool.

\begin{table*}[t]
	\centering
	\begin{tabular}{|c|c|c|c|c|}
		\hline
		Application Column  & Application & Private information leaked                       \\
		\hline
		Finance App         & Alipay      & Alipay account, personal assets(blance)          \\
		\hline
		Social  Finance App & WeChat      & WeChat account, blance, chat history             \\
		\hline
		Social App          & QQ          & QQ account, interpersonal nexus, chat history    \\
		\hline
		Social App          & Twitter     & Twitter account, interpersonal nexus             \\
		\hline
		Social App          & Gmail       & Gmail account, mail records                      \\
		\hline
		Finance App         & ICBC        & ICBC account, password, personal assets(blance)  \\
		\hline
		Finance App         & Paypal      & Paypal account, blance, bank accounts            \\
		\hline
		Tool                & Chrome      & Sites visited                                    \\
		\hline
		Tool                & Health      & personal physical metrics      					 \\
		\hline
	\end{tabular}
	\linebreak
	\caption{Information Extraction.}\shuqing{Compress.}
	\label{table:information_extracted}
\end{table*}

>>>>

In the manual analysis, we replayed the videos and extracted sensitive information.
The data we collected are listed in Table~\ref{table:information_extracted}.
Accounts of internet applications such as Apple, iCloud, Facebook, Twitter can be obtained.
Moreover, all of the typing inputs on the virtual keyboard, including the system keyboard and the built-in security keyboards of the financial applications, can be clearly recorded.
We can obtain the plain text of passwords such as WiFi passwords.
Furthermore, the received SMS verification code (usually used to confirm real-name authentication) can be obtained when it appears in the top notification bar.

In summary, though we cannot directly obtain the user's password on the lock screen, we can still check all of the information presented on the screen, extract sensitive information including but not limited to social accounts, bank accounts, personal financial situation, etc., if the user unconsciously unlocks the screen.
It is worth mentioning that {secure keyboards} built in financial apps show their keyboard typing sequences, which can be easily captured by \tool.

\begin{table*}[t]
	\centering
	\begin{tabular}{|c|c|c|c|c|}
		\hline
		\textbf{Application Column}  & \textbf{Application} & \textbf{Sensitive information leaked}                      \\
		\hline
		Finance App         & Alipay      & Alipay account, personal assets(blance)          \\
		\hline
		Social  Finance App & WeChat      & WeChat account, blance, chat history             \\
		\hline
		Social App          & QQ          & QQ account, interpersonal nexus, chat history    \\
		\hline
		Social App          & Twitter     & Twitter account, interpersonal nexus             \\
		\hline
		Social App          & Gmail       & Gmail account, mail records                      \\
		\hline
		Finance App         & ICBC        & ICBC account, password, personal assets(blance)  \\
		\hline
		Finance App         & Paypal      & Paypal account, blance, bank accounts            \\
		\hline
		Tool                & Chrome      & Sites visited                                    \\
		\hline
		Tool                & Health      & personal physical metrics      					 \\
		\hline
	\end{tabular}
	\linebreak
	\caption{Information Extraction via Manual Analysis.}\shuqing{Compress.}
	\label{table:information_extracted}
\end{table*}
